\vspace{-.2em}
\primaryline
\vspace{-.2em}
\begin{center}
    {\LARGE \textbf{\course\hspace{5px}\exam}\\
\vspace{-.2em}
 {\Large Exam Instructions}   
\end{center}

\primaryline

\noindent{Please read the information and instructions below and sign at the bottom of the page to indicate that you have done so.  If you have questions regarding the information or instructions, please ask for help before you begin the exam.}
\section*{Exam Info}
\begin{itemize}
\item This exam contains \numquestions\ questions for a total of \numpoints\ points.  Your score will be multiplied by 3.5 before it is entered in the gradebook.
\item The time limit is \TimeLimit.
\item Your name and ID number are pre-filled on the front page of this exam and your first initial, last name, and the last three digits of your ID number are on the odd numbered pages.  Please make sure you have the correct exam booklet.
\end{itemize}

\section*{Exam Resources}
\begin{itemize}
\item You may use a \textbf{SCIENTIFIC} calculator. Graphing calculators are \textbf{NOT} allowed.
\item \textbf{No other scratch paper, notes, or reference materials are allowed.}
\item All smart devices (cell phones, watches, etc.), audio devices (headphones, earbuds, etc.), and other internet and communication devices must be put away for the duration of the exam.
\end{itemize}

\section*{Work \& Answers}
\begin{itemize}
\item Please place your answer in the space provided.  Otherwise, please place a box around your answer where appropriate.
\item Show all work leading to your answer in the space provided with the problem in the exam booklet. 
\begin{itemize}
\item Mysterious or unsubstantiated answers will earn no credit. 
\item Incorrect answers with partially correct work may still earn partial credit.
\item Work shown on scratch paper will not be assessed.
\end{itemize}
\end{itemize}

\vspace{1em}
\uplevel{I have read the instructions on this page.
\vspace{4em}\\

\fillin\fillin}\\
\noindent{Signature}